\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{multirow}
\usepackage[american]{babel}
\usepackage{color}
\usepackage{balance}


\newcommand{\dl}[1]{\textcolor{blue}{{David says: {#1}}}}
\newcommand{\ml}[1]{\textcolor{red}{{Ming says: {#1}}}}
\newcommand{\xh}[1]{\textcolor{brown}{{Xuan says: {#1}}}}
\newcommand{\ft}[1]{\textcolor{green}{{Ferdian says: {#1}}}}
\newcommand{\TRANPCNN}{TRANP-CNN }

\settopmatter{printacmref=false} % Removes citation information below abstract
%\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers


\begin{document}
\title{Deep Transfer Bug Localization}

\begin{abstract}
Many projects often receive more bug reports than what they can handle. To help debug and close bug reports, a number of bug localization techniques have been proposed. These techniques analyze a bug report and return a ranked list of potentially buggy source code files. Recent development on bug localization has resulted in the construction of effective supervised approaches that use historical data of manually localized bugs to boost performance. Unfortunately, as highlighted by Zimmermann et al., sufficient bug data is often unavailable for many projects and companies. This raises the need for {\em cross-project bug localization} -- the use of data from a project to help locate bugs in another project. To fill this need, we propose a deep transfer learning approach for cross-project bug localization. Our proposed approach named \TRANPCNN\ extracts transferable semantic features from source project and fully exploits labeled data from target project for effective cross-project bug localization. We have evaluated \TRANPCNN\ on curated bug datasets from Herzig et al. and Kochhar et al. Our experiments show that averaging across the datasets, \TRANPCNN\ can locate buggy files correctly at top-1, top-5, and top-10 positions for 38.22\%, 44.88\%, 52.78\% of the bugs respectively. It can outperform a state-of-the-art bug localization solution based on deep learning and several other advanced alternative solutions by 61.13\% to 349.61\% considering various standard evaluation metrics.
\end{abstract}

\maketitle

\section{Introduction}\label{sec.intro}
\input{intro}

\section{Background}\label{sec.background}
\input{background}
	
\section{Proposed Approach}\label{sec.approach}
\input{approach}

\section{Experiments}\label{sec.exp}
\input{exp}

\section{Discussion}\label{sec.discuss}
\input{discuss}

\section{Related Work}\label{sec.related}
\input{relatedwork}

\section{Conclusion and Future Work}\label{sec.conclusion}
\input{conclusion}

\vspace{0.2cm}\noindent{\bf Acknowledgement and Replication Package.} Acknowledgement and link to replication package are omitted for double blind submission.

%\pagebreak
\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{ICSE18}

\end{document}
