%\dl{Ferdian, please add details on why the RQs are interesting and the purpose of the RQs}

Our experiments are designed to address the following research questions:

\vspace{0.2cm}\noindent\textit{\textbf{RQ1}: Is there a need for a specialized technique for cross-project bug localization?}

If a model learned from one project can be used for others project, then there is no need for a specialized technique for cross-project bug localization. Thus, before we consider other research questions, we validate the need for our proposed approach by empirically evaluating the effectiveness of a model learned from one project to localize bugs in other projects.

\vspace{0.2cm}\noindent\textit{\textbf{RQ2}: Does the cross-project feature fusion layer improve the bug localization performance?}

\dl{Xuan, please help to motivate this research question. I can't motivate it since I believe the details of the approach is going to change.}

In Section 3, we propose to employ heterogeneous predicting layers adaptation that apply two fully-connected networks for prediction from source and target projects separately, which is the key part of TRANP-CNN. In this research question, we evaluate whether the heterogeneous predicting adaptation layers help improve the bug localization performance by comparing the results previous NPCNN and SimpleTrans model. 

\vspace{0.2cm}\noindent\textit{\textbf{RQ3}: Can TRANP-CNN outperform other bug localization methods?}

A number of bug localization methods have been proposed in the literature. In this research question, we evaluate whether and to what extent can our proposed approach TRANP-CNN outperforms the state-of-the-art methods designed for bug localization and those that can be adapted for bug localization. 